\documentclass{cv}
\usepackage[margin=0.75in]{geometry}
\usepackage{paracol,lipsum}
\usepackage{color}
\usepackage{hyperref}
\thispagestyle{empty}
\begin{document}
%\familydefault
\name{Benjamin Greene}
\noindent\contact{1601 Tijeras NE \#27}{Albuquerque}{New Mexico}{benjamin.k.greene@gmail.com}{818.486.9409}
% ----------------------- Left Column --------------------
\columnratio{0.3}
\begin{paracol}{2}
\begin{raggedright}
\section{Relevant Skills}
\subsection{Language}
\bpt{Proficient in Spanish and Russian}
\subsection{Programming}
\begin{closeitems}
\item Python, C, Java
\item scheme, Bash, Latex PostgreSQL
\item Scrum, Continuous Integration
\item Git, test-driven development
\end{closeitems}
\subsection{Other Skills}
\begin{closeitems}
\item Creative 3D printing and physical prototyping
\item Significant experience with Kali linux
\item Formal training in book preservation, repair, and archiving
\item Formal training in typesetting, printing, and metalsmithing
\end{closeitems}
\subsection{Links}
\begin{closeitems}
\item \href{http://www.linkedin.com/in/benjaminkgreene}{LinkedIn:// \small{benjaminkgreene}}
\item \href{http://www.github.com/alcofrisbas}{Git:// \small{alcofrisbas}}
\item \href{http://www.dichromalogue.com}{Website \small{dichromalogue.com}}
\end{closeitems}
\subsection{Interests and Passions}
\begin{closeitems}
\item I love applying my CS coursework to linguistics problem sets; coding tools to solve other problems is really satisfying.
\item Tinkering, both physically and in code makes me tick.
\item I enjoy making esoteric languages. On my github, you can find \textbf{backpackr}, a language I made.
\end{closeitems}
\end{raggedright}
% ----------------------- Right Column --------------------
\switchcolumn
\section{Education}
\datedsubsection{Carleton College}{2015--2019}
BA: Computer Science\\
Relevant Coursework: Software Design, Database Systems, Syntactic Theory, Linguistic Field Methods, Diachronic Linguistics, Graph Theory, Computer Graphics, Machine Learning, Computational Models of Learning, NLP
\section{Experience}
\possubsection{Sandia}{Year Round Intern}{2018-Present}
\workitems{Develop and worked with data analysis toolkits in foreign language analysis}{Implement fast forward deployed analytics software and research graph-related data-processing methods}
\bpt{Research machine learning techniques for synthesizing and analyzing network data}
\possubsection{Datrium}{ Extern}{December, 2017}
\workitems{Learned about scalable cloud data storage and open convergence server infrastructure.}{Assisted in front-end web app bug fixing.}
\possubsection{Realitone Inc.}{Programmer}{2017-2018}
\workitems{Designed software to process audio samples}{Created algorithms primarily in Python to seamlessly splice and loop sounds for use in a vocal synthesizer.}
\datedsubsection{Independent Book Repair Business}{2017-2019}
\workitems{Worked with clients on personal library upkeep, including appraisals, repair, protective services, and referrals.}{Provided instruction for clients that want to learn more about book preservation.}
\section{Awards}
\datedsubsection{Larson Fellowship for Photojournalism in Latin America}{2017}
\workitems{Explored the impact of European culture in modern day South America by interviewing and capturing portraits of individuals in Peru, Ecuador, and Colombia.}{Photo essay and exhibition in Carleton College Athenaeum.}
\end{paracol}
\end{document}
