\documentclass{cv}
\usepackage[margin=0.75in]{geometry}
\usepackage{paracol,lipsum}
\usepackage{color}
\usepackage{hyperref}
\thispagestyle{empty}
\begin{document}
%\familydefault
\name{Benjamin Greene}
\noindent\contact{300 N College Street}{Northfield}{Minnesota}{greeneb2@carleton.edu}{818.486.9409}
\columnratio{0.3}
\begin{paracol}{2}
\begin{raggedright}
\section{Relevant Skills}
\subsection{Language}
\bpt{Proficient in Spanish and Russian}
\subsection{Programming}
\begin{closeitems}
\item Python, Scheme, Java
\item C, Bash, Latex, Prolog PostgreSQL
\item Project Management
\item Git, test-driven development
\end{closeitems}
\subsection{Other Skills}
\begin{closeitems}%[topsep=0pt, parsep=0pt, itemsep=0pt]
\item Creative 3D printing and physical prototyping
\item Significant experience with Arch and Kali linux
\item Formal training in book preservation, repair, and archiving
\item Formal training in typesetting and printing
\end{closeitems}
\subsection{Links}
\begin{closeitems}
\item \href{http://www.linkedin.com/in/benjaminkgreene}{LinkedIn:// \small{benjaminkgreene}}
\item \href{http://www.github.com/alcofrisbas}{Git:// \small{alcofrisbas}}
\item \href{http://www.dichromalogue.com}{Website \small{dichromalogue.com}}
\end{closeitems}
\subsection{Interests and Passions}
\begin{closeitems}
\item I love applying my CS coursework to linguistics problem sets; coding tools to solve other problems is really satisfying.
\item Tinkering, both physically and in code makes me tick.
\item I enjoy making esoteric languages. On my github, you can find \textbf{backpackr}, a language I made.
\end{closeitems}
\end{raggedright}
% ----------------------- Right Column --------------------
\switchcolumn
\section{Education}
\datedsubsection{Carleton College}{2015--Present}
BA: Computer Science -- Anticipated June 2019\\
Relevant Coursework: Software Design, Computer Organization and Architecture, Language Design and Implementation, Computer Security, Syntactic Theory, Linguistic Field Methods, Diachronic Linguistics
\section{Experience}
\possubsection{Sandia}{Intern}{Summer 2018}
\workitems{Developed and worked with data analysis toolkits in foreign language analysis}{Implemented fast forward deployed analytics software}
\possubsection{Datrium}{ Extern}{December, 2017}
\workitems{Learned about scalable cloud data storage and open convergence server infrastructure.}{Assisted in front-end web app bug fixing.}
\possubsection{Realitone Inc.}{Programmer}{2017}
\workitems{Designed software to process audio samples}{Created algorithms primarily in Python to seamlessly splice and loop sounds for use in a vocal synthesizer.}
\datedsubsection{Independent Book Repair Business}{2017-present}
\workitems{Work with clients on personal library upkeep, including appraisals, repair, protective services, and referrals.}{Provide instruction for clients that want to learn more about book preservation.}
\section{Awards}
\datedsubsection{Larson Fellowship for Photojournalism in Latin America}{2017}
\workitems{Explored the impact of European culture in modern day South America by interviewing and capturing portraits of individuals in Peru, Ecuador, and Colombia.}{Photo essay and exhibition in Carleton College Athenaeum.}
\end{paracol}
\end{document}
